Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-24 R0V0.tex
Finish to propagate the notation of the Xi set to the proof and add a statement in the proof regarding Gc

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}. In particular, given a graph $\mathscr{G}_c$ describing the communication network among different controllers
\end{theorem}

@@

\mypara 	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

>>>>

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\mypara 	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^n)$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.

	To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$. This concludes the proof of Theorem~\ref{thm:main result}.
\end{proof}
